Hyperbolic SMC: a Variational Proposal for Sequential Monte Carlo Phylogenetic Inference

### 2024-07-31 paper/paper.tex
Break hyp smc into three tasks

The central idea behind Hyperbolic SMC is to parameterize the branch length distributions by embedding the biological sequences into a hyperbolic latent space, such that distances in this space correspond roughly to evolutionary distances between sequences. The Hyperbolic SMC proposal can be explained in three parts:

\begin{enumerate}
  \item How are biological sequences (tree tips) embedded into latent space?
  \item Given the embeddings of the $N$ tree tips, and prescribed a tree topology, how are the $N-1$ internal nodes embedded?
  \item For a given branch, how do the embeddings of the two terminal nodes determine the distribution from which the branch length is sampled?
\end{enumerate}

>>>>

The central idea behind Hyperbolic SMC is to parameterize the branch length distributions by embedding the biological sequences into a hyperbolic latent space, such that distances in this space correspond roughly to evolutionary distances between sequences. The Hyperbolic SMC proposal can be broken into three main tasks:

\begin{enumerate}
  \item Embed biological sequences (tree tips) into latent space.
  \item Given the embeddings of the $N$ tree tips, and prescribed a tree topology, derive embeddings for the $N-1$ internal nodes.
  \item Sample branch lengths from a distribution parameterized by the embeddings of the two terminal nodes.
\end{enumerate}

% TODO explain why hyperbolic space is a good choice for tree embeddings
